Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2023-09-29 manuscript.RMD
update of figure legend for fig 3

**Figure 3:** Changes in protein content. A) Fold-change pre-post in levels of protein in placebo and glucose + fold-change difference 95% CI, with representative western blots of the respective proteins. Protein samples were analyzed in two duplicates per biopsy per time point, loaded on separate gels in an inverted order, e.g. from gel 3 to 6, as shown by the duplicates (1 and 2). Changes in protein levels were calculated as log-fold change scores normalized by pools (pool of all protein samples per gel). Mean log fold-change scores of the duplicates were calculated before modelling and reverse-transformed for figure visualisation. Values are estimated marginal means fold change per leg per supplement ± 95% CI. Glucose n = 13, placebo n = 13. B) Representative total protein stain blot. C) Linear relationship between total RNA (ng x mg) and UBF levels (SD units), with time added as a covariate. Total RNA was normalized by wet muscle weight, and UBF was normalized by pools per gel and total protein per lane factor. Values are presented as log-transformed means.

>>>>

**Figure 3:** Changes in c-Myc, UBF and RPS6 protein content from pre- to post-training in Placebo and Glucose conditions together with differences between conditions (second axis in a). Representative western blots of the respective proteins are shown under each panel together with total protein stains in (b). Protein samples were analyzed in two duplicates per biopsy per time point, loaded on separate gels in an inverted order as exemplified by the duplicates (1 and 2 in a and b). Values are estimated fold change per condition with 95% CI, Glucose n = 13 and placebo n = 13. A linear relationship was shown between between total RNA (ng x mg) and UBF levels (SD units) while controlling for time. Total RNA was normalized by wet muscle weight, and UBF was normalized by a pooled sample used on each gel.
